### 2020-05-22 Documents/Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200203093818.tex
Reorganised Git

    This suggestion aims to build upon the work presented by Hu et al. \cite{Hu2019} in which the
    point is made that the vast majority of the work done in this area considers games with a finite
    (usually two) number of agents. This limits the capability of the analysis to generalise to much
    larger agent populations, such as swarms. To allieviate this concern, the authors present an
    anaysis of the learning dynamics for a large agent population (which they approximate as
    containing infinite agents) where each agent is an independent Q-Learning using Boltzmann
    exploration. The emergent dynamics is given by a Fokker-Planck equation which is numerical shown
    to be a strong approximation of the true learning dynamics. However, as the authors point out,
    this is the first attempt at considering such a problem, and relies on heavy assumptions.
    Possible extensions therefore require a consideration of:

    \begin{itemize}
        \item Asymmetric games, in which agents have different payoffs, introducing heterogeneity
        and competition into the system.
        \item Stateful Games.
        \item Heterogeneous populations, in which there are p different populations of agents.
    \end{itemize}

    To the best of my knowledge, in the particular case of $N >> 1$ agent populations, none of the
    above have yet been attempted.

    \section{Continuous Action Spaces}

    Here lies the opportunity to extend the work of Tuyls' et al. \cite{Tuyls2006AnGames} towards
    continuous action spaces. This would be particularly useful for most robotic applications, which
    operate in continuous spaces.

    Work has commenced in this area, but is still in its infancy. Notable examples are: 
    \cite{Letcher2019DifferentiableMechanics}, in which Letcher et al. consider the dynamics of
    Differentiable Games, though their focus is on its application to gradient descent in GANs as
    opposed to reinforcement learning, and \cite{Galstyan2013}, in which the dynamics of Q-Learning,
    with a Boltzmann action selection is considered. To achieve the result, the author replaces the
    strategy vector with a probability density function (pdf) over the strategy space, which leads
    to an integro-differential equation which describes the evolution of the pdf with time. Due to
    its complexity, the dynamics cannot be analysed as easily as those in \cite{Tuyls2006AnGames},
    and so Galstyan restricts the analysis to the steady-state solution (i.e. the fixed point) of
    the dynamics. Their analysis shows strong agreement with the designed experiments, under varying
    payoff conditions (note that the payoffs are now a function, rather than a discrete matrix).

    Galstyan goes on to present avenues for further work. These are summarised below:

    \begin{itemize}
        \item  An analysis of the steady state equations, considering the existence and uniqueness
        of solutions under varying payoff structures. How do these compare with the underlying Nash
        Equilibrium. Tuyls and Westra also suggest the consideration of stability analysis in this regard.
        \item A consideration of larger agent populations. No attempt towards this has yet been made
        as far as I am aware.
        \item A consideration of these dynamics under state transitions. Tuyls and Westra suggest
        that an analysis using switching dynamics (Chapter \ref{ch::ControlTheory}) may be useful
        here, but no attempt has yet been made as far as I am aware.
    \end{itemize}

    Tuyls and Westra \cite{TuylesWestra} also consider continuous action spaces from the same
    perspective as Ruijgrok and Ruijgrok \cite{Ruijgrok}, namely that of the replicator dynamics.
    The former extend the analysis of the latter by considering the case where mutations are
    deterministic (e.g. through epsilon-greedy exploration) and these mutations only allow for small
    changes within the strategy space. From an EGT perspective, this analysis provides a strong
    characterisation of learning dynamics in continous action spaces and generalises the results of
    Galstyan to generic update rules (rather than the traditional Q-Learning approach).

    \section{Stateful environments} \label{sec::Stateful}

    This is potentially the most relevant of the sections in regards to applicability to
    reinforcement learning as it extends the typical consideration of stateless normal-form games,
    in which the payoffs and strategies of each player is well defined, to stochastic games, in
    which games have probabilistic transitions across them. I have yet to explore this section in
    depth.

    \section{Characterisation of Complex Dynamics}

    The intention of this area of study is to consider the ideas presented in works such as 
    \cite{Sanders2018} and \cite{Galla2011} which consider complex behaviour, including cycles and
    chaos, in certain games using simple reinforcement learning algorithms. These provide a great
    deal of insight into whether or not the game will converge and, if so, to what equilibrium.
    Galla, for instance, shows that adjusting a memory parameter when learning to solve an Iterated
    Prisoner's Dilemma game can shift the equilibrium from one showing purely defective behaviour to
    one showing cycles of cooperations and defection. Sanders et al. generalise this result by
    showing that, for a particular learning algorithm known as Experience Weighted Attraction,
    learning dynamics varies dependent on the mutual effect of two parameters.

    This determination of where RL algorithms will show complex dynamics is important, not only for
    a priori understanding of resultant behaviour, but is particularly important for algorithms in
    which agents aim to predict the behaviour of other agents. For this to be feasible, the learning
    dynamics must not exhibit chaos, otherwise it would be impossible for an agent to make any
    reasonable predictions about the future behaviour of its opponents.

>>>>

    This suggestion aims to build upon the work presented by Hu et al. \cite{Hu2019} in which the
    point is made that the vast majority of the

### 2020-05-22 Documents/Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200203153437.tex
Reorganised Git

    \begin{itemize}
        \item  An analysis of the steady state equations, considering the existence and uniqueness
        of solutions under varying payoff structures. How do these compare with the underlying Nash
        Equilibrium. Tuyls and Westra also suggest the consideration of stability analysis in this regard.
        \item A consideration of larger agent populations. No attempt towards this has yet been made
        as far as I am aware.
        \item A consideration of these dynamics under state transitions. Tuyls and Westra suggest
        that an analysis using switching dynamics (Chapter \ref{ch::ControlTheory}) may be useful
        here, but no attempt has yet been made as far as I am aware.
    \end{itemize}

    Tuyls and Westra \cite{TuylesWestra} also consider continuous action spaces from the same
    perspective as Ruijgrok and Ruijgrok \cite{Ruijgrok}, namely that of the replicator dynamics.
    The former extend the analysis of the latter by considering the case where mutations are
    deterministic (e.g. through epsilon-greedy exploration) and these mutations only allow for small
    changes within the strategy space. From an EGT perspective, this analysis provides a strong
    characterisation of learning dynamics in continous action spaces and generalises the results of
    Galstyan to generic update rules (rather than the traditional Q-Learning approach).

>>>>

    \begin{itemize}
        \item  An analysis of the steady state equations, considering the existence and uniqueness
        of solutions under varying payoff structures. How do these compare with the underlying Nash
        Equilibrium.
        \item A consideration of larger agent populations. No attempt towards this has yet been made
        as far as I am aware.
        \item A consideration of these dynamics under state transitions. Tuyls and Westra suggest
        that an analysis using switching dynamics (Chapter \ref{ch::ControlTheory}) may be useful
        here, but no attempt has yet been made as far as I am aware.
    \end{itemize}

### 2020-05-22 Documents/Literature Review/Literature Review - Revised/.history/sections/GameTheory_20200106085934.tex
Reorganised Git

>>>>

\section{Game Dynamics}

Game Dynamics (which I often refer to as Multi Agent Dynamics or Learning Dynamics) considers the
problem of mathematically modelling Multi Agent Systems who repeatedly interact with one another.
This model then serves to be able to predict the evolution of the system as well as to understand
the trajectory of learning. Typically, this looks at considering whether or not the method is likely
to converge towards a Nash equilibrium. This is generally a difficult problem to solve
\cite{ShohamMultiagentFoundations} for all but toy problems. To extend this applicability into real
world settings requires the study of stable equilbrium points;
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world environments.

\TODO{Add in the papers from Mendeley which are useful to this part of the study}

### 2020-05-22 Documents/Literature Review/Literature Review - Revised/sections/MARL.tex
Reorganised Git

\section{Learning Dynamics}

Learning Dynamics (which I often refer to as Multi Agent Dynamics or Game Dynamics) considers the
problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
another. This model then serves to be able to predict the evolution of the system as well as to
understand the trajectory of learning. Typically, this looks at considering whether or not the
method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
solve \cite{ShohamMultiagentFoundations} for all but toy problems.
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world environments.

The area of dynamics which has shown most promise in Multi-Agent Reinforcement Learning is that of
evolutionary dynamics. This draws from the principles of Evolutionary Game Theory (EGT) which
considers similar assumptions to that of MARL: agents are no longer required to be rational and play
the game optimise their expected return through repeated play. Importantly, players have no
knowledge of the others' payoffs \cite{Tuyls2006AnGames}. The first major breakthrough in this field
is in \cite{Borgers1997} where Boergers and Sarin determine the relation between the replicator
dynamics concept of EGT (a differential equation defining the evolution of the proportion of a
subgroup in an evolving population) and the 'Cross' learning method for multi agent reinforcement
learning. This idea is advanced in \cite{Tuyls2006AnGames} where Tuyls et al. determine  a similar
relation for Q-Learning using Boltzmann probabilities as Q-values. The result was a dynamics
equation which describes, for each action, the evolution of its selection probability which could
even account for random exploration. There have since been a number of works which apply the same
insight into different game types and MARL algorithms. In \cite{Bloembergen2015}, these are broken
into the following categories

@@

Though the above have seen success through experimental validation, most work is applied to bimatrix
games (games of two to three players with finite action spaces). An example of this can be found in
\cite{Hofbauer1996} in which Hofbauer shows that learning a zero-sum bimatrix game follows
Hamiltonian dynamics and results in stable equilibria. Recent work has begun the consideration of
improving the models towards more complex scenarios with larger agent populations. For instance,
Bailey and Piliouras show in \cite{Bailey2019Multi-AgentSystem} that the results of
\cite{Hofbauer1996} can be extended to the n-agent case, even with different network structures.
They show that the result generalises to any zero-sum network game where agents use a
Follow-The-Regularised-Leader learning approach. Another, more recent example of this is 
\cite{Hu2019}, in which Hu uses a mean field approximation to model the dynamics of a population of
Q-Learning agents. As a reminder, mean field (MF) approaches in MARL consider that an agent updates
its strategy based on the mean effect of the population. The result is a system of three equations
which describes the evolution of Q-values over a large population in a symmetric bi-matrix game.This
presents an important first step in modelling the learning dynamics of large agent populations and
has the scope to be expanded to systems of asymmetric games, heterogeneous populations and stateful
n-agent games.

An advantage of determining the evolutionary dynamics of learning is that it can describe the
expected behaviour using different learning methodologies for various game settings. This is
particularly important to understand the convergence of the applied learning method; certain games
will often show cyclic behaviour even with the existence of a strict NE. For instance, Imhof et al.
show in \cite{Imhof2005} that a repeated prisoner's dilemma game results in cyclic behaviour when
considering the options of cooperation or defection. In an interesting twist, Galla shows in
\cite{Galla2011} that this result is dependent on the memory of the agent. Therefore, by using a
method of batch learning, in which agents may discount observations from the distant past, the
agents will move their convergent result from a stict NE (to always defect) to a mixed, stable
equilibrium which promotes cooperation. In \cite{Sanders2018}, Sanders et al. extend this approach
to a general n-player game which is learnt through an experience-weighted attraction method. They
show that the method will display different dynamical behaviour including: convergence to stable
equilibria, limit cycles and chaos. They determine a parameter which describes the likelihood of
complex dynamics and show that, as the number of players increase, the likelihood of complex
dynamics (which will not converge to fixed points) will increase. A similarly interesting result is
that of chaotic dynamics in certain game types and learning algorithms. Sato et al show in
\cite{Sato2002} that Cross learning in two person games result in choatic behaviour and use the
simple rock-paper-scissors game to illustrate this point. In \cite{Foster2001}, Foster and Young
show that in these games, agents cannot learn the future behaviour of their opponents, regardless of
the learning technique. This therefore means that the game does not converge to a NE.

The above discussion highlights just some of the growing body of work regarding the dynamics of
multi-agent learning. It is clear that these studies provide strong insights into the prevalent
problem of multi agent systems, particularly those using reinforcement learning. It allows for an
analysis of the conditions under which learning is possible as well as a method to evaluate
different learning algorithms. However, this field still requires significant work in terms of
generality. A proposal to expand this research is presented in 'Proposed Research'.

>>>>

\section{Game Dynamics}

Game Dynamics (which I often refer to as Multi Agent Dynamics or Learning Dynamics) considers the
problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
another. This model then serves to be able to predict the evolution of the system as well as to
understand the trajectory of learning. Typically, this looks at considering whether or not the
method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
solve \cite{ShohamMultiagentFoundations} for all but toy problems.
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world environments.

The area of dynamics which has shown most promise in Multi-Agent Reinforcement Learning is that of
evolutionary dynamics. This draws from the principles of Evolutionary Game Theory (EGT) which
considers similar assumptions to that of MARL: agents are no longer required to be rational and
play the game optimise their expected return through repeated play. Importantly, players have no
knowledge of the others' payoffs \cite{Tuyls2006AnGames}. In \cite{Tuyls2006AnGames}, Tuyls et al.
determine the relation between the replicator dynamics concept of EGT (a differential equation
defining the evolution of the proportion of a subgroup in an evolving population) and Q-Learning
using Boltzmann probabilities as Q-values. The result was a dynamics equation which describes, for
each action, the evolution of its selection probability which could even account for random
exploration. There have since been a number of works which apply the same insight into different
game types and MARL algorithms. In \cite{Bloembergen2015}, these are broken into the following
categories

@@

Though the above have seen success through experimental validation in games with 2 players and (in
general) 2 to 3 discrete actions, recent work has begun the consideration of improving the models
towards more complex scenarios with larger agent populations. A recent example of this is 
\cite{Hu2019}, in which Hu uses a mean field approximation to model the dynamics of a population of
Q-Learning agents. As a reminder, mean field (MF) approaches in MARL consider that an agent updates
its strategy based on the mean effect of the population. The result is a system of three equations
which describes the evolution of Q-values over a large population in a symmetric bi-matrix game.This
presents an important first step in modelling the learning dynamics of large agent populations and
has the scope to be expanded to systems of asymmetric games, heterogeneous populations and stateful
games.

An advantage of determining the evolutionary dynamics of learning is that it can describe the
expected behaviour in different game settings. This is particularly important to understand the
convergence of the methods; certain games will often show cyclic behaviour even with the existence
of a strict NE. For instance, Imhof et al. show in \cite{Imhof2005} that a repeated prisoner's
dilemma game results in cyclic behaviour when considering the options of cooperation or defection.
